CLT extension visuals

### 2022-05-16 analysis/clt_irt_analysis.Rmd
add model params item selection
add model params

```{r}
irt1 <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "logit"),
  correct ~ 1 + (1 | targetWord) + (1 | subjID),
  prior = prior_1pl,
  control = list(adapt_delta = 0.9),
  cores = 6,
  chains = 6,
  iter = 6000
)

irt1 <- add_criterion(irt1, "loo")

@@

```{r}
irt2 <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "logit"),
  bf(
    correct ~ exp(logalpha) * eta,
    eta ~ 1 + (1 |i| targetWord) + (1 | subjID),
    logalpha ~ 1 + (1 |i| targetWord),
    nl = TRUE
  ),
  prior = prior_2pl,
  control = list(adapt_delta = 0.9, max_treedepth = 12),
  cores = 6,
  chains = 6,
  iter = 6000
)

irt2 <- add_criterion(irt2, "loo")

@@

```{r}
irt3 <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "identity"),
  bf(
    correct ~ 0.25 + 0.75 * inv_logit(exp(logalpha) * eta),
    eta ~ 1 + (1 |i| targetWord) + (1 | subjID),
    logalpha ~ 1 + (1 |i| targetWord),
    nl = TRUE
  ),
  prior = prior_va_3pl,
  control = list(adapt_delta = 0.9, max_treedepth = 12),
  cores = 6,
  chains = 6,
  iter = 6000
)

irt3 <- add_criterion(irt3, "loo")

@@

pp_check(irt3)
```

@@

#saveRDS(params_joy, "../saves/model_params_irt3_draws.rds")

ggplot(params_joy, aes(y = reorder(item, -aoa_german_comb), x = val, fill = aoa_german_comb))+
  geom_density_ridges(size = 0.2,scale = 4, alpha = .5)+
  facet_grid(~nlpar, scales = "free_x")+
  labs(y = "Item")+
  scale_fill_viridis_c(name = "AoA")+
  theme_minimal()

params_joy%>%
  group_by(nlpar)%>%
  summarise(min = min(val), 
            max = max(val))
```

@@

@@

```{r}
irt3_dif_sex <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "identity"),
  bf(
    correct ~ 0.25 + 0.75 * inv_logit(exp(logalpha) * eta),
    eta ~ 1 + (0+ sex  |i| targetWord) + (1 | subjID),
    logalpha ~ 1 + (0+ sex  |i| targetWord),
    nl = TRUE
  ),
  control = list(adapt_delta = 0.9, max_treedepth = 12),
  prior = prior_va_3pl,
  cores = 6,
  chains = 6,
  iter = 6000
)

irt3_dif_sex <- add_criterion(irt3_dif_sex, "loo")

@@

irt3_dif_sex <- readRDS("../saves/irt3_dif_sex.rds")
```

@@

```{r}
irt3_dif_order <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "identity"),
  bf(
    correct ~ 0.25 + 0.75 * inv_logit(exp(logalpha) * eta),
    eta ~ 1 + (0+ order  |i| targetWord) + (1 | subjID),
    logalpha ~ 1 + (0+ order  |i| targetWord),
    nl = TRUE
  ),
  control = list(adapt_delta = 0.9, max_treedepth = 12),
  prior = prior_va_3pl,
  cores = 6,
  chains = 6,
  iter = 6000
)

irt3_dif_order <- add_criterion(irt3_dif_order, "loo")

>>>>

```{r}
irt1 <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "logit"),
  correct ~ 1 + (1 | targetWord) + (1 | subjID),
  prior = prior_1pl,
  control = list(adapt_delta = 0.95, max_treedepth = 12),
  cores = 6,
  chains = 6,
  iter = 6000
)%>%add_criterion(c("loo","waic"))

@@

```{r}
irt2 <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "logit"),
  bf(
    correct ~ exp(logalpha) * eta,
    eta ~ 1 + (1 |i| targetWord) + (1 | subjID),
    logalpha ~ 1 + (1 |i| targetWord),
    nl = TRUE
  ),
  prior = prior_2pl,
  control = list(adapt_delta = 0.95, max_treedepth = 12),
  cores = 6,
  chains = 6,
  iter = 6000
)%>%add_criterion(c("loo","waic"))

@@

```{r}
irt3 <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "identity"),
  bf(
    correct ~ 0.25 + 0.75 * inv_logit(exp(logalpha) * eta),
    eta ~ 1 + (1 |i| targetWord) + (1 | subjID),
    logalpha ~ 1 + (1 |i| targetWord),
    nl = TRUE
  ),
  prior = prior_va_3pl,
  control = list(adapt_delta = 0.95, max_treedepth = 12),
  cores = 6,
  chains = 6,
  iter = 6000
)%>%add_criterion(c("loo","waic"))

@@

pp_check(irt3)

pairs(irt3)
```

@@

saveRDS(params_joy, "../saves/model_params_irt3_draws.rds")

ggplot(params_joy, aes(y = reorder(item, -aoa_german_comb), x = val, fill = aoa_german_comb))+
  geom_density_ridges(size = 0.2,scale = 4, alpha = .5)+
  facet_grid(~nlpar, scales = "free_x")+
  labs(y = "Item")+
  scale_fill_viridis_c(name = "AoA")+
  theme_minimal()
```

@@

#saveRDS(icc3, "../saves/icc_3PL.rds")

@@

```{r}
irt3_dif_sex <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "identity"),
  bf(
    correct ~ 0.25 + 0.75 * inv_logit(exp(logalpha) * eta),
    eta ~ 1 + (0+ sex  |i| targetWord) + (1 | subjID),
    logalpha ~ 1 + (0+ sex  |i| targetWord),
    nl = TRUE
  ),
  control = list(adapt_delta = 0.95, max_treedepth = 12),
  prior = prior_va_3pl,
  cores = 6,
  chains = 6,
  iter = 6000
)%>%add_criterion(c("loo","waic"))

@@

irt3_dif_sex <- readRDS("../saves/irt3_dif_sex.rds")

@@

```{r}
irt3_dif_order <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "identity"),
  bf(
    correct ~ 0.25 + 0.75 * inv_logit(exp(logalpha) * eta),
    eta ~ 1 + (0+ order  |i| targetWord) + (1 | subjID),
    logalpha ~ 1 + (0+ order  |i| targetWord),
    nl = TRUE
  ),
  control = list(adapt_delta = 0.95, max_treedepth = 12),
  prior = prior_va_3pl,
  cores = 6,
  chains = 6,
  iter = 6000
)%>%add_criterion(c("loo","waic"))

### 2022-05-16 analysis/clt_item_selection.Rmd
add model params

params_order <- readRDS("../saves/model_params_irt3_dif_order.rds")%>%
  select(-uci, -lci)%>%
  pivot_wider(names_from = order, values_from = mode)%>%
  mutate(order_dif = A-B)
```

@@

for (j in 1:6) {

@@

sim_size%>%
  ggplot(aes(x = factor(size), y = cor))+
  geom_point(pch = 1)+
  geom_line(aes(group = factor(iter), lty = factor(iter)))+
  theme_minimal()+
  labs(x = "No. of items", y = "Correlation with full test")

@@

sim_size_age%>%
  ggplot(aes(x = factor(size), y = cor, col = factor(age_group)))+
  geom_point(pch = 1)+
  geom_line(aes(group = interaction(age_group,factor(iter)), lty = factor(iter)))+
  theme_minimal()+
  #facet_grid(factor(iter)~.)+
  labs(x = "No. of items", y = "Correlation with full test")+
  scale_color_colorblind(name = "Age group")

@@

   sim <- simulated_annealing(15)

@@

icc3 %>% 
  filter(item %in% frq_sel_items)%>%
  #filter(item == "orchid")%>%
  ggplot(aes(x = theta, y = p,group = item, col = aoa_german_comb)) +
  #geom_line() +
  geom_line(col = "firebrick", alpha = .5) +
  #geom_textline(aes(label = item)) +
  #geom_texthline(yintercept = 0.25, lty = 3, alpha = .75, label = "guessing",hjust = 0.8)+
  geom_hline(yintercept = 0.25, lty = 3, alpha = .75)+
  #facet_wrap(~group)+
  guides(col = F)+
  scale_color_viridis_c(name = "AoA") +
  labs(#title = "ICCs for selected items",
       x = expression(theta~('ability on the logit scale')),
       y = expression(italic(p)(y==1))) +
  ylim(0,1)+
  theme_minimal()
```
## Correaltion selected with full test

>>>>

# params_order <- readRDS("../saves/model_params_irt3_dif_order.rds")%>%
#   select(-uci, -lci)%>%
#   pivot_wider(names_from = order, values_from = mode)%>%
#   mutate(order_dif = A-B)
```

@@

@@

sim_size%>%
  ggplot(aes(x = factor(size), y = cor))+
  geom_point(pch = 1)+
  geom_line(aes(group = factor(iter), lty = factor(iter)))+
  scale_linetype(name = "Run")+
  theme_minimal()+
  labs(x = "No. of items", y = "Correlation with full test")

@@

sim_size_age%>%
  ggplot(aes(x = factor(size), y = cor, col = factor(age_group)))+
  geom_point(pch = 1)+
  geom_line(aes(group = interaction(age_group,factor(iter)), lty = factor(iter)))+
  theme_minimal()+
  scale_linetype(name = "Run")+
  #facet_grid(factor(iter)~.)+
  labs(x = "No. of items", y = "Correlation with full test")+
  scale_color_colorblind(name = "Age group")

@@

   sim <- simulated_annealing(20)

@@

icc3 %>% 
  filter(item %in% frq_sel_items)%>%
  #mutate(sel = ifelse(item %in% frq_sel_items, "a", "b"))%>%
  #filter(item == "orchid")%>%
  ggplot(aes(x = theta, y = p,group = item, col = aoa_german_comb)) +
  #geom_line(alpha = .5) +
  #geom_line(col = "firebrick", alpha = .5) +
  geom_textline(aes(label = item)) +
  #geom_texthline(yintercept = 0.25, lty = 3, alpha = .75, label = "guessing",hjust = 0.8)+
  geom_hline(yintercept = 0.25, lty = 3, alpha = .75)+
  #facet_wrap(~group)+
  guides(col = F)+
  scale_color_viridis_c(name = "AoA") +
  #scale_color_manual(values = c("firebrick", "grey"))+
  labs(#title = "ICCs for selected items",
       x = expression(theta~('ability on the logit scale')),
       y = expression(italic(p)(y==1))) +
  ylim(0,1)+
  theme_minimal()
```
## Correaltion selected with full test

### 2022-05-16 analysis/clt_visuals.Rmd
add model params

---
title: "CLT item selection"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggpubr)
library(ggthemes)
```

@@

# params_order <- readRDS("../saves/model_params_irt3_dif_order.rds")%>%
#   select(-uci, -lci)%>%
#   pivot_wider(names_from = order, values_from = mode)%>%
#   mutate(order_dif = A-B)
```

# Differential item functioning

```{r}
# exclude items based on differential item functioning
## Split by sex
params_sex_p <- params_sex%>%
  group_by(nlpar)%>%
  mutate(sd = sd(sex_dif), 
         cut_low = mean(sex_dif)-2*sd,
         cut_high = mean(sex_dif)+2*sd)

ggplot(params_sex_p, aes(x = sex_dif))+
  geom_vline(aes(xintercept = cut_low), lty = 3, alpha = .75)+
  geom_vline(aes(xintercept = cut_high), lty = 3, alpha = .75)+
  geom_histogram(col = "black", alpha = .5)+
  facet_grid(~nlpar)+
  theme_minimal()

ggplot(params_sex_p, aes(x = sex_dif, label = item, y = reorder(item, abs(sex_dif))))+
  geom_vline(aes(xintercept = cut_low), lty = 3, alpha = .75)+
  geom_vline(aes(xintercept = cut_high), lty = 3, alpha = .75)+
  geom_point(col = "black", alpha = .5)+
  facet_grid(~nlpar)+
  theme_minimal()

exclude_sex <- params_sex_p%>%
  filter(sex_dif < cut_low | sex_dif > cut_high)%>%
  pull(item)

## Split by Order
### not necessary since model comparison says order adds no predictive value

# params_order_p <- params_order%>%
#   group_by(nlpar)%>%
#   mutate(sd = sd(order_dif), 
#          cut_low = mean(order_dif)-2*sd,
#          cut_high = mean(order_dif)+2*sd)
# 
# ggplot(params_order_p, aes(x = order_dif))+
#   geom_vline(aes(xintercept = cut_low), lty = 3, alpha = .75)+
#   geom_vline(aes(xintercept = cut_high), lty = 3, alpha = .75)+
#   geom_histogram(col = "black", alpha = .5)+
#   facet_grid(~nlpar)+
#   theme_minimal()
# 
# 
# ggplot(params_order_p, aes(x = order_dif, label = item, y = reorder(item, abs(order_dif))))+
#   geom_vline(aes(xintercept = cut_low), lty = 3, alpha = .75)+
#   geom_vline(aes(xintercept = cut_high), lty = 3, alpha = .75)+
#   geom_point(col = "black", alpha = .5)+
#   facet_grid(~nlpar)+
#   theme_minimal()
# 
# exclude_order <- params_order_p%>%
#   filter(order_dif < cut_low | order_dif > cut_high)%>%
#   pull(item)
# 
# 
# model_params <- all_model_params%>%
#   filter(!item %in% exclude_sex,
#          !item %in% exclude_order)
```

```{r}
items <- model_params%>%filter(nlpar=="Easiness")%>%pull(item)
easiness <- filter(model_params, nlpar=="Easiness") %>% pull(Estimate)
easy_spread <- model_params%>%filter(nlpar=="Easiness")%>%mutate(width = abs(Q97.5 - Q2.5)) %>% pull(width)
discrimination <- filter(model_params, nlpar=="Discrimination") %>% pull(Estimate)

full <- data%>%
  group_by(subjID)%>%
  summarise(mean_full = mean(correct))
```

```{r}
easb <- tibble()

for (j in 1:100) {

for (i in 1:48) {

  x <- sample(easiness, i)

	nn_dists <- rep(0, length(x)-1)
	for(k in 1:length(x)-1) {
		nn_dists[k] <- x[k+1] - x[k]
	}

	spacing <- -1*sd(nn_dists)

	row <- tibble(iter = j,
                size = i, 
                mean = spacing/2)
  easb <- bind_rows(easb,row)
}
}

ggplot(easb, aes(x = factor(size), y = mean))+
  geom_point(pch = 1)+
  theme_minimal()

```

```{r}
discrimb <- tibble()

for (j in 1:100) {

for (i in 1:48) {
  x <- sample(discrimination, i)
  mean_x <- mean(x)
  row <- tibble(iter = j,
                size = i, 
                mean = mean_x/2)
  discrimb <- bind_rows(discrimb,row)
}
}

ggplot(discrimb, aes(x = factor(size), y = mean))+
  geom_point(pch = 1)+
  theme_minimal()

```

```{r}
spreadb <- tibble()

for (j in 1:100) {

for (i in 1:48) {
  x <- sample(easy_spread, i)
  mean_x <- mean(x)
  row <- tibble(iter = j,
                size = i, 
                mean = mean_x/5)
  spreadb <- bind_rows(spreadb,row)
}
}

ggplot(spreadb, aes(x = factor(size), y = mean))+
  geom_point(pch = 1)+
  theme_minimal()

```

```{r}
score_fn <- function(subset) {
	easinesses <- sort(easiness[subset])
	nn_dists <- rep(0, sum(subset)-1)
	for(i in 1:sum(subset)-1) {
		nn_dists[i] <- easinesses[i+1] - easinesses[i]
	}
	spacing <- -1*sd(nn_dists)
	mean_discrim <- mean(discrimination[subset])
	mean_spread <- mean(easy_spread[subset])

	# sel <- items[subset == TRUE]
	# 
	# sub_dat <- data%>%
	#   filter(targetWord %in% sel)%>%
	#   group_by(subjID)%>%
	#   summarise(mean_sub = mean(correct))
	# 
	# cor <- cor(sub_dat$mean_sub,full$mean_full)
	# 
	# return(spacing + mean_discrim/6 + cor/3)
	return(spacing + mean_discrim/2 - mean_spread/5)
}

proposal_fn <- function(subset) {
	# Randomly sample a number of swaps.
	# Prefer a small number of swaps for "fine tuning", but allow
	# occasional large numbers of swaps, including a complete
	# exchange of the subset
	subset_size = sum(as.integer(subset))
	max_swaps = min(subset_size, length(subset) - subset_size)
	swaps <- rbinom(1, max_swaps-1, 1/(max_swaps-1)) + 1

	# Choose the items to swap
	active_items <- seq(1:length(subset))[subset == TRUE]
	inactive_items <- seq(1:length(subset))[subset == FALSE]
	actives_to_swap <- sample(active_items, swaps)
	inactives_to_swap <- sample(inactive_items, swaps)

	# Do the swapping
	for(i in 1:swaps) {
		subset[actives_to_swap[i]] <- FALSE
		subset[inactives_to_swap[i]] <- TRUE
	}
	return(subset)
}

simulated_annealing <- function(k, cooling_ratio=0.999, reset_thresh=1000, break_thresh=10000) {
  easiness <- filter(model_params, nlpar=="Easiness") %>% pull(Estimate)
  easy_spread <- model_params%>%filter(nlpar=="Easiness")%>%mutate(width = abs(Q97.5 - Q2.5)) %>% pull(width)
  discrimination <- filter(model_params, nlpar=="Discrimination") %>% pull(Estimate)
	N <- length(easiness)

	current_subset <- sample(c(rep(TRUE, k), rep(FALSE, N-k)))
	best_subset <- current_subset
	best_score <- score_fn(best_subset)

	temp <- 100
	rejected <- 0
	no_new_bests <- 0
	for(i in 1:1e6) {
		# Score new subset, and toss a coin
		new_subset <- proposal_fn(current_subset)
		new_score <- score_fn(new_subset)
		accept_decrease <- rbernoulli(1, temp / 100)

		# Accept the new subset if it's an improvement, or if our
		# cooling coin came up heads.
		if(new_score > best_score | accept_decrease) {
			current_subset <- new_subset
			rejected <- 0
			if(new_score > best_score) {
				best_subset <- new_subset
				best_score <- new_score
				no_new_bests <- 0
			} else {
				no_new_bests <- no_new_bests + 1
			}
		# Quit if we've had too many rejections in a row.
		} else {
			rejected <- rejected + 1
			no_new_bests <- no_new_bests + 1
			if(rejected == break_thresh) {
				#print(best_score)
			  ret <- tibble(best_subset = list(best_subset),
	              best_score = best_score)

				return(ret)
			}
		}
		# Start random resets to the current best subset if we haven't
		# found anything better in quite a while.
		if(no_new_bests > reset_thresh & rbernoulli(1, 1/100)) {
			current_subset <- best_subset
		}

		# Cool it!
		temp <- temp*cooling_ratio
	}
	#print(best_score)
	ret <- tibble(best_subset = list(best_subset),
	              best_score = best_score)

	return(ret)
}
```

```{r, message=F, warning=F, comment=F}
sim_a <- simulated_annealing(20)

sel_items <- items[unlist(sim_a$best_subset) == TRUE]

sim_a$best_score
```

## Visualize parameters of selected items

```{r}
model_params%>%
  filter(item %in% sel_items)%>%
  ggplot(aes(reorder(item, -Estimate), Estimate, ymin = Q2.5, ymax = Q97.5)) +
	facet_wrap(~nlpar, scales = "free_x") +
	geom_pointrange() +
	coord_flip() +
	labs(x = "Item")+
  theme_minimal()
```

## Correaltion with full test

```{r}
sub2 <- data%>%
  filter(targetWord %in% sel_items)%>%
  group_by(age_group,subjID)%>%
  summarise(mean_sub = mean(correct))

comp2<- full%>%left_join(sub2)

ggplot(comp2, aes(x = mean_full, y = mean_sub))+
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = .75)+
  geom_jitter(pch = 1, alpha = .75, height = 0.01, width = 0.01)+
  stat_cor()+
  facet_wrap(~age_group)+
  ylim(0,1.02)+
  xlim(0,1.02)+
  theme_few()
```

## Variation in score

```{r, warning=FALSE}
sim_score <- tibble()

for (i in 5:35) {

  for (j in 1:10) {

   sim <- simulated_annealing(i)

   score <- tibble(score = sim$best_score, 
                   size = i,
                   iter = j)

   sim_score <- bind_rows(sim_score, score)
  }

}

sim_score%>%
  ggplot(aes(x = size, y = score, group = iter))+
  geom_point(pch = 1)+
  theme_minimal()
```

## Determine size

```{r, warning=FALSE}
sim_size <- tibble()

for (j in 1:10) {

for (i in 5:40) {

   sim <- simulated_annealing(i)

    sel <- items[unlist(sim$best_subset) == TRUE]

	sub_dat <- data%>%
	  filter(targetWord %in% sel)%>%
	  group_by(subjID)%>%
	  summarise(mean_sub = mean(correct))

	cor <- cor(sub_dat$mean_sub,full$mean_full)

	row <- tibble(size = i, 
         iter = j, 
         cor = cor)

  sim_size <- bind_rows(sim_size, row)
}

}

sim_size%>%
  ggplot(aes(x = factor(size), y = cor))+
  geom_point(pch = 1)+
  geom_line(aes(group = factor(iter), lty = factor(iter)))+
  scale_linetype(name = "Run")+
  theme_minimal()+
  labs(x = "No. of items", y = "Correlation with full test")

```

```{r, warning=FALSE}
sim_size_age <- tibble()

for (j in 1:5) {

for (i in 5:40) {

   sim <- simulated_annealing(i)

    sel <- items[unlist(sim$best_subset) == TRUE]

    cor <- data%>%
      filter(targetWord %in% sel)%>%
      group_by(age_group,subjID)%>%
  summarise(mean_sub = mean(correct))%>%
  right_join(full)%>%
  group_by(age_group)%>%
  summarise(cor = cor(mean_sub, mean_full))%>%
  mutate(size = i, 
         iter = j)

  sim_size_age <- bind_rows(sim_size_age, cor)
}

}

sim_size_age%>%
  ggplot(aes(x = factor(size), y = cor, col = factor(age_group)))+
  geom_point(pch = 1)+
  geom_line(aes(group = interaction(age_group,factor(iter)), lty = factor(iter)))+
  theme_minimal()+
  scale_linetype(name = "Run")+
  #facet_grid(factor(iter)~.)+
  labs(x = "No. of items", y = "Correlation with full test")+
  scale_color_colorblind(name = "Age group")

```

## Select items

```{r}
item_sel <- tibble()

for (i in 1:100) {

   sim <- simulated_annealing(20)

   sel <- items[unlist(sim$best_subset) == TRUE]

   it <- data%>%
     distinct(targetWord)%>%
     filter(targetWord %in% sel)%>%
     select(targetWord)%>%
     mutate(iter = i)

   item_sel <- bind_rows(item_sel, it)
}

item_sel%>%
  group_by(targetWord)%>%
  summarise(n = n()/max(iter))%>%
  ggplot(aes(x = reorder(targetWord, -n), y = n))+
  geom_bar(stat = "identity", col = "black", fill = "white")+
  labs(x = "Item", y = "Proportion selected")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## ICC for subset

```{r}
frq_sel_items <- item_sel%>%
  group_by(targetWord)%>%
  summarise(n = n()/max(iter))%>%
  arrange(-n)%>%
  slice(1:20)%>%
  pull(targetWord)

icc3 %>% 
  filter(item %in% frq_sel_items)%>%
  #mutate(sel = ifelse(item %in% frq_sel_items, "a", "b"))%>%
  #filter(item == "orchid")%>%
  ggplot(aes(x = theta, y = p,group = item, col = aoa_german_comb)) +
  #geom_line(alpha = .5) +
  #geom_line(col = "firebrick", alpha = .5) +
  geom_textline(aes(label = item)) +
  #geom_texthline(yintercept = 0.25, lty = 3, alpha = .75, label = "guessing",hjust = 0.8)+
  geom_hline(yintercept = 0.25, lty = 3, alpha = .75)+
  #facet_wrap(~group)+
  guides(col = F)+
  scale_color_viridis_c(name = "AoA") +
  #scale_color_manual(values = c("firebrick", "grey"))+
  labs(#title = "ICCs for selected items",
       x = expression(theta~('ability on the logit scale')),
       y = expression(italic(p)(y==1))) +
  ylim(0,1)+
  theme_minimal()
```
## Correaltion selected with full test

```{r}
subsel <- data%>%
  filter(targetWord %in% frq_sel_items)%>%
  group_by(age_group,subjID)%>%
  summarise(mean_sub = mean(correct))

compsel<- full%>%left_join(subsel)

ggplot(compsel, aes(x = mean_full, y = mean_sub))+
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = .75)+
  geom_jitter(pch = 1, alpha = .75, height = 0.01, width = 0.01)+
  stat_cor()+
  #facet_wrap(~age_group)+
  labs(#title = "ICCs for selected items",
       x = "Full test - proportion correct",
       y = "Short test - proportion correct") +
  ylim(0,1.02)+
  xlim(0,1.02)+
  theme_few()
```

```{r}
model_params%>%
  filter(item %in% frq_sel_items)%>%
  ggplot(aes(reorder(item, -Estimate), Estimate, ymin = Q2.5, ymax = Q97.5)) +
	facet_wrap(~nlpar, scales = "free_x") +
	geom_pointrange() +
	coord_flip() +
	labs(x = "Item")+
  theme_minimal()
```

>>>>

---
title: "CLT extension visuals"
output: html_document
---
```{r setup, include=FALSE}
library(tidyverse)
library(ggpubr)
library(ggthemes)
```

@@

icc3 <- readRDS("../saves/icc_3PL.rds")
```

```{r}
all_model_params%>%
  filter(nlpar == "Easiness")%>%
  ggplot(aes(x = Estimate, y = aoa_german_comb))+
  #geom_abline(intercept = 0, slope = 1, lty = 2, alpha = .75)+
  geom_point()+
  stat_cor()
```
